### 2016-05-26 R/ITHIM.Rmd
Update to ITHIM.Rmd

```{r instantiate}
ITHIM <- list(
  parameters = parameters <- createParameterList(),
  means = means <- computeMeanMatrices(parameters),
  quintiles = quintiles <- getQuintiles(means)
)
```

>>>>

```{r instantiate}
ITHIM.baseline <- list(
  parameters = parameters <- createParameterList(baseline = TRUE),
  means = means <- computeMeanMatrices(parameters),
  quintiles = quintiles <- getQuintiles(means)
)
ITHIM.scenario <- list(
  parameters = parameters <- createParameterList(baseline = FALSE),
  means = means <- computeMeanMatrices(parameters),
  quintiles = quintiles <- getQuintiles(means)
)

RR <- createActiveTransportRRs()
RR <- matrix(RR$BreastCancer[,"F"],nrow=nAgeClass,ncol = 5, byrow = FALSE)

totalMETs.baseline <- mapply("+",ITHIM.baseline$quintiles$TotalTravelMET,computeNonTravelMETs(),SIMPLIFY=FALSE)
totalMETs.scenario <- mapply("+",ITHIM.scenario$quintiles$TotalTravelMET,computeNonTravelMETs(),SIMPLIFY=FALSE)

RR^(totalMETs$F^0.5)
